Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
edited introduction

\subsection{Main Results}
\begin{enumerate}
	\item Petri's Theorem
	\item Modular Forms
	\item Stacky Relations
\end{enumerate}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
$R(\sx,\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
\ldots, e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has relations in degree at most
$\max(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
for signatures with $g = 0$.
\end{thm}
\todo{Say that this follows immediately from the three theorems for the special cases.}
Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].

@@

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbf{N}$ such
that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}
In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
\end{itemize}
\end{lem}

@@

\begin{lem}
\label{lem:sat_two_induction}
Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$.  Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

In a fashion analogous to the proof of Lemma 
~\ref{lem:sat_three_induction}, we see 
the following is a $k$ basis for $R$ over $R'$:

\begin{lem}
\label{lem:sat_two_induction}
\todo{Make explicit assumptions on genus.}
\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction. Actually, the map isn't ramified at $P$, it's just defined away from $P$. I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

@@

\iffalse{
\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

We prove an inductive theorem on adding 2-sat here.

\begin{cor}
Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
\end{cor}
\begin{proof}
For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
\end{proof}

}
\fi

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Lemma ~\ref{lem:sat_three_induction} and
an inductive statement on ramification orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Now we can induct on cases (a)-(k) of \ref{lem:g_0_admissible_cases}
to obtain bounds on the minimal generator and relation degrees for
canonical rings of curves in the genus 0 case.

Through the application of two processes of induction, by adding 
points via Lemma ~\ref{lem:sat_three_induction} and by raising
ramification orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

\begin{center}
\label{table:g_0_exceptional}
\textbf{Table (IV)}: Genus 0 exceptional cases
\end{center}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
so long as $\sigma$ does not lie in a finite list of exceptional
cases, as listed in Table ~\ref{table:g_0_exceptional}.
\end{thm}

\begin{proof}
If $\sx$ has no ramification points, then we have the classical
case which is done in Chapter 4 of Voight and Zureick-Brown
\cite{vzb:stacky}.

Now let us consider the case when $\delta \geq 2$. In this case,
$\halfcan$ is an effective divisor. \todo{need to do this case}

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
and not one of the exceptional cases in Table
~\ref{table:g_0_exceptional}.

If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.

So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
where $\sigma'$ has $r$ many ramification points all of order $3$
and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
all of the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
If $r \leq 5$, then $\sigma$ ``lies above'' one of the base cases
of Lemma ~\ref{lem:g_0_admissible_cases}, all of which satisfy
the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.

So for any $r > 0$, there is a $(\sigma', J)$, either from
Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
the $r > 5$ case with ramification orders all $3$, with $\sigma' =
(0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.

All such base cases satisfy all of the hypotheses of
Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
(d) that the relations are generated up to degree $2e$.

>>>>

\subsection{Main Results}
\begin{enumerate}
	\item Modular Forms
	\todo{Reference independence of base field}
\end{enumerate}

Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is well known that the sheaf $\Omega_X,$ with associated divisor $K_X$ determines the {\bf canonical map} $\pi:X \rightarrow \BP_k^{g-1}.$ Then, the {\bf canonical ring}, is defined as
\begin{align*}
	R(X,K_X) = \bigoplus_{n \geq 0} H^0(X,nK_X),
\end{align*}
with multiplication structure corresponding to tensor product of sections. Since $\Omega_X$ is ample, $X \cong \proj R$. Petri's theorem gives generators and relations for $R(X,K_X),$ see for example, \cite{saint-donat:proj}[Theorem, p. 157], showing that in most cases $R(X,K_X)$ is generated in degree 1 with relations in degree 2. This has the pleasant geometric consequence that all such canonically embedded curves are scheme theoretically cut out by quadratic equations.

In Voight and Zureick-Brown, \cite{vzb:stacky} examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf ramification order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
\end{align*}
The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
$R(\sx,\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
\ldots, e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has relations in degree at most
$\max(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
for signatures with $g = 0$.
\end{thm}
\todo{Say that this follows immediately from the three theorems for the special cases.}
Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].

@@

\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

Transition to genus one.
\todo{transition!}

\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
We prove an inductive theorem on adding 2-sat here.
\todo{description}

\begin{prop}
\label{prop:sat_two_induction}
Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

In a fashion analogous to the proof of Proposition 
~\ref{prop:sat_three_induction}, we see 
the following is a $k$ basis for $R$ over $R'$:

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
generator $u$ in degree 1.  Suppose $D$ is generated by $
u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
that

\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}
In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
\end{itemize}
\end{lem}

@@

\begin{cor}
Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
\end{cor}
\begin{proof}
For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
\end{proof}

\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
\label{ssec:g_0_ram_pts}

\begin{prop}
\label{prop:sat_three_induction}
\todo{Make explicit assumptions on genus.}
\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction. Actually, the map isn't ramified at $P$, it's just defined away from $P$. I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

@@

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Proposition ~\ref{prop:sat_three_induction} and
an inductive statement on ramification orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Now we can induct on cases (a)-(e) of \ref{lem:g_0_admissible_cases}
to obtain bounds on the minimal generator and relation degrees for
canonical rings of curves in the genus 0 case.

Through the application of two processes of induction, by adding 
points via Proposition ~\ref{prop:sat_three_induction} and by raising
ramification orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

\begin{center}
\label{table:g-0-exceptional}
\textbf{Table (IV)}: Genus 0 exceptional cases
\end{center}

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
finite list of exceptional cases, as listed in Table
~\ref{table:g-0-exceptional}.
\end{thm}

\begin{proof}

%By Lemma ~\ref{lem:g_0_admissible_cases}, we know that for
%any tame log spin curves $(\sx', \Delta, \halfcan')$ over a perfect
%field $k$ with signature $\sigma'$ and set $J$ such that $(\sigma',
%J)$ is one of the listed base cases, $(\sigma', J)$ is admissible.
%Furthermore, $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k
%$- algebra by elements of degree at most $e = \max(5, e_1, \ldots, e
%_r)$ with relations in degree at most $2e$. It also admits a
%presentation
%
%\begin{align*}
	%R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
%\end{align*}
%
%\noindent
%given by admissibility satisfying the statements that for all $i \in 
%J$, $e_i > \deg z$ for any generator $z$ of $R'$ and that $in_\prec
%(I')$ is minimally generated by products of two monomials under
%some ordering.
%
%Then we can apply two processes of induction, by adding points via
%Proposition ~\ref{prop:sat_three_induction} and by raising
%ramification orders via Theorem ~\ref{thm:ram_order_ind},
%to obtain the desired result for any tame log spin curve $(\sx,
%\Delta, L)$ over a perfect field $k$ with signature $\sigma$
%covered by this induction process.
%
%
%
%A process of induction raising the ramification orders of
%the ramified points of the spin curves corresponding to Lemma
%~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
%~\ref{thm:ram_order_ind} will demonstrate the desired generator and
%relation degree results for curves with three ramified points.
%Similarly, this induction process on Lemma
%~\ref{lem:g_0_admissible_cases} case (d) will give the desired
%result for curves with four ramified points excluding signature
%$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
%number of ramified points via Proposition
%~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
%case (e) combined with the induction process on ramification orders
%will yield the result for curves with at least five ramified points.
\end{proof}
